### 2019-12-06 paper1/article.tex
Adding Paper 2 (in progress).
Modified reference style.

In the field of colloidal science, much progress has been made on the synthesis of elementary building blocks \Ge{(Fig.\ \ref{fig:exp})} mimicking molecular structures to elaborate innovative materials, \eg materials with complete three dimensional band gaps \cite{Xia_etal_AM2000, Velev_etal_AM2009, Li_etal_AC2011, Sacanna_etal_COCIS2011}. The basic elements of such colloidal molecules are particles or droplets less than one millimeter in size, and their self-assembly relies on either lengthy brownian motion or careful microfludic designs, on top of typical colloidal interactions, \eg depletion attraction and electrostatic repulsion \cite{Mewis_colloidal, Yi_etal_CM2013, Shen_AS_2016}. Regardless of the approach, however, questions remain why the colloidal particles/droplets undergo certain path to organize themselves and how such process can be controlled and optimized. Since full data are not yet accurately accessible from experiments in such miniature systems, computer simulations will be useful to provide supplemental information.

@@

Scaling down to microscale appears first to be a convenience for the numerical simulations of multicomponent and multiphase systems as the non-linear Navier-Stokes (NS) equations can be reduced to the linear Stokes equations. This allows the use of boundary integral methods (BIM) \cite{Pozrikidis}, \eg most recently the GGEM-based BIM \cite{Kumar_JCP_2012, Lailai_SM_2014} solving the Stokes equations in general geometries. However, it is also possible to use the conventional unsteady, fractional-step/projection-method NS solver at low Reynolds number, combined with an interface description method \cite{Worner_2012, Galusinski_JCP_2008}. The latter approach is more versatile, probably less difficult to implement, and enjoys a rich literature of standard numerical techniques. Here, in view of a rich range of possible applications and considering also the rapid development of inertial microfluidics (where inertial effects are used to better control the flow behavior) we take the approach of simulating the incompressible, two-fluid NS as outlined in \cite{Dodd_JCP_2014}. The splitting procedure proposed in \cite{Dodd_JCP_2014} enables the use of fast solvers for the pressure Poisson equation also for large density and viscosity contrasts. The remaining choice then is to be made among the available interface-description methods.

Generally, there are two categories of methods to resolve an interface in a NS solver, \ie front-tracking methods and front-capturing methods. An example of the front-tracking method is the immersed boundary method (IBM) \Ge{\cite{Peskin,Uhlmann}. Using Lagrangian points in a moving frame, IBM can offer a high interface resolution without the need to deform the underlying mesh in the fixed frame. However, the coupling of the two meshes relies on a regularized delta function, which introduces certain degrees of smearing. Moreover, large interface deformation requires frequent mesh rearrangement; and topology changes may have to be handled manually. These constraints make IBM typically more expensive and less appealing for droplet simulations.}

Front-capturing methods, on the other hand, are Eulerian and handle topology changes automatically; they are therefore easier to parallelize to achieve higher efficiency. One of such methods is the volume-of-fluid (VOF) method \cite{Scardovelli_ARFM_1999}, which defines different fluids with a discontinuous color function. The main advantage of VOF is its intrinsic mass conservation. It suffers however from inaccurate computations of the interface properties, \eg normals and curvatures. This makes it less favorable for simulations of microfluidic systems where surface tension \Ge{is the dominant effect and requires accurate modelling.}

Another popular front-capturing method is the level set (LS) method \cite{Sethian_levelset, Sussman_JCP_1994}. Contrary to VOF, LS prescribes the interface through a \Ge{(Lipschitz-)continuous} function which usually takes the form of the signed distance to the interface. \Ge{Under this definition}, normals and curvatures of the interface can be readily and accurately computed. However, the problem when simulating incompressible flows is that mass loss/gain may occur and accumulate because the LS function embeds no volume information. \Ge{In addition, errors can also arise from solving the LS advection equation and/or the reinitialization equation,} a procedure commonly required to reshape the LS into a distance function. Therefore, additional measures have to be taken to ensure mass conservation.

Many different approaches have been proposed to make LS mass-conserving, which can be classified into the following \Ge{four} methodologies. The first approach is to improve the LS discretization and reinitialization so that numerical errors are reduced. In practice, one can increase the order of LS fluxes \cite{Nourgaliev_JCP_2007}, minimize the displacement of the zero LS during reinitialization \Ge{\cite{Russo_JCP_2000,Nourgaliev_JCP_2007}}, or employ local mesh refinement \Ge{\cite{Strain_JCP_1999b,Min_JCP_2007,Herrmann_JCP_2008}}. By doing so, mass loss can be greatly reduced, although the LS function is still inherently non-conservative. The second remedy couples the LS with \Ge{a conservative description (\eg VOF) or Lagrangian particles.} For example, \Ge{the hybrid particle level set method \cite{Enright_JCP_2002},} the coupled level set volume-of-fluid (CLSVOF) method \cite{Sussman_JCP_2000}, the mass-conserving level set (MCLS) method \cite{Pijl_CVS_2008}, or the recent curvature-based mass-redistribution method \cite{Luo_JCP_2015}. With varying level of coupling, \Ge{these methods can usually preserve mass really well; the drawback is that the complexity and some inaccuracy (due to interpolation, reconstruction, \etc) of the other method will be imported. The third approach improves mass conservation by adding a volume-constraint in the LS or NS formulation. Examples of this kind include the interface-preserving LS redistancing algorithm \cite{Sussman_JSC_1997} and the mass-preserving NS projection method \cite{Salac_CPC_2016}. Finally, one can also smartly modify the definition of the LS, such as the hyperbolic-tangent level set \cite{Olsson_JCP_2005}, to reduce the overall mass loss.}
%the extension-velocity level set \cite{Sabelnikov_JCP_2014},

@@

\Ge{Provided a mass-preserving level set method, the coupled flow solver must also accurately compute the surface tension, a singular effect of the normal stress on the interface. This is particularly important for microfluidic systems; as surface tension scales linearly with the dimension, it decays slower than volumetric forces (\eg gravity) when the size of the system reduces.}
%One difficulty of the simulation of multiphase flow is the presence of surface tension, which manifests itself as a pressure jump across an infinitesimally thin interface. In microfluidic systems, particularly, surface tension becomes more prominent since it scales linearly with the dimension of the system (hence diminishes slower than volumetric forces such as gravity).  
To handle such discontinuities, one approach is the continuum surface force (CSF) \cite{Brackbill_JCP_1992}, \Ge{originally developed for the VOF method, later extended to the LS \cite{Sussman_JCP_1994}.} 
%which smears out the pressure difference and models the surface tension as a smoothed forcing term. 
\Ge{Although easy to implement}, CSF effectively introduces an artificial spreading of the interface \Ge{by regularizing the pressure difference}, and it can become erroneous when two interfaces are within its smoothing width.
%Another interesting technique, in the context of finite-difference discretizations of the NS equations, 
\Ge{A second, non-smearing approach is the ghost fluid method (GFM). Proposed initially for solving compressible Euler equations \cite{Fedkiw_JCP_1999}, GFM provides a finite-difference discretization of the gradient operator even if the stencil includes shocks. It has been proven to converge \cite{Liu_MC_2003} and was soon applied for treating the pressure jump in multiphase flows \cite{Kang_JSC_2000}. We note that although the GFM can be reformulated in a similar way to the CSF \cite{Lalanne_JCP_2015,Popinet_ARFM_2018}, its treatment for discontinuous quantities is sharp in the finite difference limit.}

\Ge{Several implementation options of the GFM were suggested in \cite{Kang_JSC_2000,Lalanne_JCP_2015,Desjardins_JCP_2008}. Here, we follow the methodology of \cite{Desjardins_JCP_2008}, \ie using the GFM for the pressure jump due to surface tension while neglecting the viscous contribution. As will be discussed later, this choice is especially suitable for microfluidic applications where the capillary effect is strong.}
% result in a second-order accurate pressure field, while preserving the discontinuity for both pressure and density. Their original algorithm is framed for solving the pressure Poisson equation iteratively, \eg through a multi-grid solver. Here, we first propose a second-order accurate, grid-converging interface curvature estimation, and then adapt it to a fast pressure-correction method (FastP*) \cite{Dodd_JCP_2014} that benefits from an efficient, FFT-based, direct solver. The only additional requirement from \cite{Dodd_JCP_2014} is that the computational domain is periodic in at least two directions. 
\Ge{To efficiently solve for the pressure, we further combine the GFM with a fast pressure-correction method (FastP*) \cite{Dodd_JCP_2014}. Such a combination enables a direct solve of the pressure Poisson equation using the Gauss elimination in the Fourier space; it is the most efficient when the computational domain is periodic, but it also applies to a range of homogeneous Dirichlet/Neumann boundary conditions via fast sine/cosine transforms \cite{Schumann_JCP_1988}, see \eg a recent open-source distribution \cite{Pedro_CaNS}. Using a second-order accurate, grid-converging interface curvature estimation, we will show that the coupled ICLS/NS solver can handle large density/viscosity contrasts and converges between first and second order in both space and time.}

Finally, a unique challenge to the simulation of colloidal droplets is the modeling of near-field interactions. It is known that two or more colloids can interact via dispersion, surface, depletion, and hydrodynamic forces \cite{Mewis_colloidal}. Apart from the hydrodynamic forces which is determined directly from the NS, and the dispersion forces which arise from quantum mechanical effects, the depletion and surface forces must be modelled. These forces can be either attraction or repulsion and are typically calculated from the gradient of a potential.
\Ge{Based on colloidal theory, we propose a novel hydrodynamic model for the depletion force in the framework of the ICLS/NS solver. Our method relies on two extensions: \textit{i)} extending the single level set (SLS) function to multiple level set (MLS) functions; and \textit{ii)} extending the GFM for computation of the gradient of depletion potential. 
MLS has the benefits that each droplet within a colloidal cluster can be treated individually, is allowed to interact with the other droplets, and is guarded from its own mass loss. MLS also prevents numerical coalescence of droplets when they get too close. The computational complexity, proportional to the number of MLS functions ($l$) and the number of cells in each dimension ($N$), is higher than SLS. However, we note that many techniques exist to reduce the CPU cost and/or memory consumption if $lN^d$ ($d=$ 2 or 3) is large. For detailed implementations of such optimized algorithms we refer to \cite{Peng_JCP_1999,Nielsen_JSC_2006,Brun_JCP_2012}. In the present paper, we will demonstrate the self-assembly of colloidal droplets using one droplet per MLS function.}
%Hence, MLS is needed to determine the interaction forces. Combining with GFM, we propose a novel method to compute the near field interactions in our NS solver. The GFM makes the interaction force sharp and the MLS makes it possible for two droplets to be closer than one grid cell without automatic merging.

@@

\noindent where ${\bm u}={\bm u}({\bm x},t)$ is the velocity field, $p=p({\bm x},t)$ is the pressure field, and $\bm{g}$ is a unit vector aligned with gravity or buoyancy. $\rho_i$ and $\mu_i$ are the density and dynamic viscosity ratios of fluid $i$ ($i=1$ or $2$) and the reference fluid. These properties are \Ge{constant in each phase and} subject to a jump across the interface, which we denote as $[\rho]_\Gamma=\rho_2-\rho_1$ for density and $[\mu]_\Gamma=\mu_2-\mu_1$ for viscosity. For viscous flows, the velocity and its tangential derivatives are continuous on the interface \cite{Liu_JCP_1994}. However, the pressure is discontinuous due to the surface tension and the viscosity jump, \ie
\begin{equation}
    [p]_\Gamma = \frac{1}{We} \kappa + \frac{2}{Re}[\mu]_\Gamma {\bm n}^T \cdot \nabla {\bm u} \cdot {\bm n},
  \label{pressure jump}
\end{equation}
\noindent where $\kappa$ is the interface curvature, and ${\bm n}$ is the normal to the interface.  
If the surface tension coefficient, $\tilde{\sigma}$, varies on the interface the tangential stress is also discontinuous. In this paper, we assume constant and uniform $\tilde{\sigma}$. In Eqs.\ \eqref{NS} and \eqref{pressure jump}, Re, We, and Fr are, respectively, the Reynolds, Weber, and Froude numbers, defined as
\begin{equation}
  \begin{aligned}
    Re = \frac{\tilde{\rho_1} \tilde{U} \tilde{L}}{\tilde{\mu_1}},\quad \quad We = \frac{\tilde{\rho_1} \tilde{U}^2 \tilde{L}}{\tilde{\sigma}},\quad \quad Fr=\frac{\tilde{U}^2}{\tilde{g}\tilde{L}},      
  \label{non-di}    
  \end{aligned}
\end{equation}
\noindent where $\tilde{U}$, $\tilde{L}$, $\tilde{\rho_1}$, $\tilde{\mu_1}$, and $\tilde{g}$ denote the reference dimensional velocity, length, density, dynamic viscosity, and gravitational acceleration. Note that $\rho_1=1$ and $\mu_1=1$ (i.e.\ we define fluid 1 as the reference fluid).

@@

The motion of a fluid interface is governed by the following PDE
\begin{equation}
  \frac{\partial \phi}{\partial t} + {\bm u} \cdot \nabla \phi = 0,
  \label{ls adv}
\end{equation}
where ${\bm u}$ is the flow velocity field. Despite of its simple form, obtaining an accurate and robust solution to Eq.\ \eqref{ls adv} is challenging. For two-fluid problems, state-of-the-art level set transport schemes include the high-order upstream-central (HOUC) scheme \cite{Nourgaliev_JCP_2007}, the weighted essentially non-oscillatory (WENO) scheme \cite{Liu_JCP_1994}, \Ge{the semi-Lagrangian scheme \cite{Strain_JCP_1999}}, or the semi-jet scheme \cite{Velmurugana_AX_2016}. Quantitative comparisons of these schemes in various test cases can be found in \cite{Nourgaliev_JCP_2007, Velmurugana_AX_2016}. We note that the choice of the scheme is case-dependent, \ie depending on the smoothness of the overall level set field or the stiffness of Eq.\ \eqref{ls adv}. For flows involving moderate deformations, HOUC is usually sufficient and most efficient. For more complex flows, WENO or semi-Lagragian/jet schemes combined with grid refinement might be pursed. In the present study, we use either HOUC5 or WENO5 (5 denotes fifth-order accuracy) to evaluate $\nabla \phi$.

%In general, a nonlinear hyperbolic system can be solved with finite difference methods, including total-variation-diminishing (TVD), total-variation-bounded (TVB), essentially non-oscillatory (ENO) \cite{Harten_JCP_1987}, and weighted essentially non-oscillatory (WENO) \cite{Liu_JCP_1994} schemes. These methods have been developed to obtain stable and, in the case of ENO or WENO, high-order-accuracy solutions at the appearance of strong discontinuities, see \eg the text of Lax \cite{Lax_1970} and LeVeque \cite{LeVeque_hyperbolic}, or the lecture notes in high-order methods for computational physics edited by Barth and Deconinck \cite{Barth_notes_computational}. Specifically, 
\sloppy
For the temporal discretization of Eq.\ \eqref{ls adv}, we use a three-stage total-variation-diminishing (TVD) third-order Runge-Kutta scheme \cite{Shu_JCP_1988}. Denoting $f(\phi)=-{\bm u} \cdot \nabla \phi$, it updates $\phi$ from time level $n$ to $n+1$ in three sub-steps
\begin{equation}
  \begin{cases}
    & \phi^1 = \phi^n + \Delta t \cdot f(\phi^n)  \\
    & \phi^2 = \frac{3}{4} \phi^n + \frac{1}{4} \phi^1 + \frac{1}{4} \Delta t \cdot f(\phi^1) \\
    & \phi^{n+1} = \frac{1}{3} \phi^n + \frac{2}{3} \phi^2 + \frac{2}{3} \Delta t \cdot f(\phi^2). \\
  \end{cases}
  \label{SSP-RK3}
\end{equation}
%where $f(\phi)=-{\bm u} \cdot \nabla \phi$. %On a standard staggered grid where scalars are defined at cell centers and vectors are defined at cell faces, $f(\phi)$ is computed at cell centers by using central averaging for ${\bm u}$ and a finite difference method for $\nabla \phi$. For the spatial derivatives $\nabla \phi$, instead of using the abovementioned ENO or WENO schemes, we note that the smoothness of $\phi$ and the linearity of its advection Eq.\ \eqref{ls adv} allows the use of simpler and more efficient upwinding schemes, such as the high order upstream central (HOUC) discretizations. Detailed descriptions of HOUC and its comparisons with WENO in the level set framework for interface tracking can be found in \cite{Nourgaliev_JCP_2007, Desjardins_JCP_2008}. Based on these reports and our tests, we use the HOUC5 to evaluate $\nabla \phi$. As a final note, although HOUC5 is fifth-order accurate, the overall accuracy of $\phi$ is second-order due to central averaging of the velocity field at cell centers.

\Ge{Finally, we note that Eq.\ \eqref{ls adv} does not need to be solved in the entire computational domain, as only the near-zero values are used to identify the interface and compute its curvature. This motivated the so-called narrow band approach \cite{Adalsteinsson_JCP_1995, Peng_JCP_1999}, which localizes the level set to the interface using index arrays. Combined with optimal data structures \cite{Nielsen_JSC_2006,Brun_JCP_2012}, fast computation and low memory footprint may be achieved at the same time. In our implementation, we store all the level set values while only update those in a narrow band, \ie solving $\phi_t+c(\phi){\bm u}\cdot \nabla \phi=0$ with the cut-off function given as}
\begin{equation}
  c(\phi) =
  \begin{cases}
     1 & \textrm{if} \quad  |\phi| < \gamma \\
     0 & \textrm{otherwise}, \\
  \end{cases}
  \label{NB cut-off}
\end{equation}
\Ge{where $\gamma= 6\Delta x$ as additional distance information is required to model droplet interactions (Sec.\ \ref{sec: idrop}). This is equivalent to \cite{Peng_JCP_1999} with a simplified $c(\phi)$.}

@@

%Curvature computation is crucial to interfacial flows in the presence of surface tension \cite{Herrmann_JCP_2008, Desjardins_JCP_2008}, and even more so in our case, when we apply curvature-dependent interface corrections. Inaccurate curvature can result in unphysical spurious currents, as will be shown in Sec.\ \ref{sec: spurious}. 
From Eq.\ \eqref{curv}, the curvature $\kappa$ can be evaluated as

>>>>

In the field of colloidal science, much progress has been made on the synthesis of elementary building blocks \Ge{(Fig.\ \ref{fig:exp})} mimicking molecular structures to elaborate innovative materials, \eg materials with complete three dimensional band gaps \citep{Xia_etal_AM2000, Velev_etal_AM2009, Li_etal_AC2011, Sacanna_etal_COCIS2011}. The basic elements of such colloidal molecules are particles or droplets less than one millimeter in size, and their self-assembly relies on either lengthy brownian motion or careful microfludic designs, on top of typical colloidal interactions, \eg depletion attraction and electrostatic repulsion \citep{Mewis_colloidal, Yi_etal_CM2013, Shen_AS_2016}. Regardless of the approach, however, questions remain why the colloidal particles/droplets undergo certain path to organize themselves and how such process can be controlled and optimized. Since full data are not yet accurately accessible from experiments in such miniature systems, computer simulations will be useful to provide supplemental information.

@@

Scaling down to microscale appears first to be a convenience for the numerical simulations of multicomponent and multiphase systems as the non-linear Navier-Stokes (NS) equations can be reduced to the linear Stokes equations. This allows the use of boundary integral methods (BIM) \citep{Pozrikidis}, \eg most recently the GGEM-based BIM \citep{Kumar_JCP_2012, Lailai_SM_2014} solving the Stokes equations in general geometries. However, it is also possible to use the conventional unsteady, fractional-step/projection-method NS solver at low Reynolds number, combined with an interface description method \citep{Worner_2012, Galusinski_JCP_2008}. The latter approach is more versatile, probably less difficult to implement, and enjoys a rich literature of standard numerical techniques. Here, in view of a rich range of possible applications and considering also the rapid development of inertial microfluidics (where inertial effects are used to better control the flow behavior) we take the approach of simulating the incompressible, two-fluid NS as outlined in \cite{Dodd_JCP_2014}. The splitting procedure proposed in \cite{Dodd_JCP_2014} enables the use of fast solvers for the pressure Poisson equation also for large density and viscosity contrasts. The remaining choice then is to be made among the available interface-description methods.

Generally, there are two categories of methods to resolve an interface in a NS solver, \ie front-tracking methods and front-capturing methods. An example of the front-tracking method is the immersed boundary method (IBM) \Ge{\citep{Peskin,Uhlmann}. Using Lagrangian points in a moving frame, IBM can offer a high interface resolution without the need to deform the underlying mesh in the fixed frame. However, the coupling of the two meshes relies on a regularized delta function, which introduces certain degrees of smearing. Moreover, large interface deformation requires frequent mesh rearrangement; and topology changes may have to be handled manually. These constraints make IBM typically more expensive and less appealing for droplet simulations.}

Front-capturing methods, on the other hand, are Eulerian and handle topology changes automatically; they are therefore easier to parallelize to achieve higher efficiency. One of such methods is the volume-of-fluid (VOF) method \citep{Scardovelli_ARFM_1999}, which defines different fluids with a discontinuous color function. The main advantage of VOF is its intrinsic mass conservation. It suffers however from inaccurate computations of the interface properties, \eg normals and curvatures. This makes it less favorable for simulations of microfluidic systems where surface tension \Ge{is the dominant effect and requires accurate modelling.}

Another popular front-capturing method is the level set (LS) method \citep{Sethian_levelset, Sussman_JCP_1994}. Contrary to VOF, LS prescribes the interface through a \Ge{(Lipschitz-)continuous} function which usually takes the form of the signed distance to the interface. \Ge{Under this definition}, normals and curvatures of the interface can be readily and accurately computed. However, the problem when simulating incompressible flows is that mass loss/gain may occur and accumulate because the LS function embeds no volume information. \Ge{In addition, errors can also arise from solving the LS advection equation and/or the reinitialization equation,} a procedure commonly required to reshape the LS into a distance function. Therefore, additional measures have to be taken to ensure mass conservation.

Many different approaches have been proposed to make LS mass-conserving, which can be classified into the following \Ge{four} methodologies. The first approach is to improve the LS discretization and reinitialization so that numerical errors are reduced. In practice, one can increase the order of LS fluxes \citep{Nourgaliev_JCP_2007}, minimize the displacement of the zero LS during reinitialization \Ge{\citep{Russo_JCP_2000,Nourgaliev_JCP_2007}}, or employ local mesh refinement \Ge{\citep{Strain_JCP_1999b,Min_JCP_2007,Herrmann_JCP_2008}}. By doing so, mass loss can be greatly reduced, although the LS function is still inherently non-conservative. The second remedy couples the LS with \Ge{a conservative description (\eg VOF) or Lagrangian particles.} For example, \Ge{the hybrid particle level set method \citep{Enright_JCP_2002},} the coupled level set volume-of-fluid (CLSVOF) method \citep{Sussman_JCP_2000}, the mass-conserving level set (MCLS) method \citep{Pijl_CVS_2008}, or the recent curvature-based mass-redistribution method \citep{Luo_JCP_2015}. With varying level of coupling, \Ge{these methods can usually preserve mass really well; the drawback is that the complexity and some inaccuracy (due to interpolation, reconstruction, \etc) of the other method will be imported. The third approach improves mass conservation by adding a volume-constraint in the LS or NS formulation. Examples of this kind include the interface-preserving LS redistancing algorithm \citep{Sussman_JSC_1997} and the mass-preserving NS projection method \citep{Salac_CPC_2016}. Finally, one can also smartly modify the definition of the LS, such as the hyperbolic-tangent level set \citep{Olsson_JCP_2005}, to reduce the overall mass loss.}
%the extension-velocity level set \citep{Sabelnikov_JCP_2014},

@@

\Ge{Provided a mass-preserving level set method, the coupled flow solver must also accurately compute the surface tension, a singular effect of the normal stress on the interface. This is particularly important for microfluidic systems; as surface tension scales linearly with the dimension, it decays slower than volumetric forces (\eg gravity) when the size of the system reduces.}
%One difficulty of the simulation of multiphase flow is the presence of surface tension, which manifests itself as a pressure jump across an infinitesimally thin interface. In microfluidic systems, particularly, surface tension becomes more prominent since it scales linearly with the dimension of the system (hence diminishes slower than volumetric forces such as gravity).  
To handle such discontinuities, one approach is the continuum surface force (CSF) \citep{Brackbill_JCP_1992}, \Ge{originally developed for the VOF method, later extended to the LS \citep{Sussman_JCP_1994}.} 
%which smears out the pressure difference and models the surface tension as a smoothed forcing term. 
\Ge{Although easy to implement}, CSF effectively introduces an artificial spreading of the interface \Ge{by regularizing the pressure difference}, and it can become erroneous when two interfaces are within its smoothing width.
%Another interesting technique, in the context of finite-difference discretizations of the NS equations, 
\Ge{A second, non-smearing approach is the ghost fluid method (GFM). Proposed initially for solving compressible Euler equations \citep{Fedkiw_JCP_1999}, GFM provides a finite-difference discretization of the gradient operator even if the stencil includes shocks. It has been proven to converge \citep{Liu_MC_2003} and was soon applied for treating the pressure jump in multiphase flows \citep{Kang_JSC_2000}. We note that although the GFM can be reformulated in a similar way to the CSF \citep{Lalanne_JCP_2015,Popinet_ARFM_2018}, its treatment for discontinuous quantities is sharp in the finite difference limit.}

\Ge{Several implementation options of the GFM were suggested in \cite{Kang_JSC_2000,Lalanne_JCP_2015,Desjardins_JCP_2008}. Here, we follow the methodology of \cite{Desjardins_JCP_2008}, \ie using the GFM for the pressure jump due to surface tension while neglecting the viscous contribution. As will be discussed later, this choice is especially suitable for microfluidic applications where the capillary effect is strong.}
% result in a second-order accurate pressure field, while preserving the discontinuity for both pressure and density. Their original algorithm is framed for solving the pressure Poisson equation iteratively, \eg through a multi-grid solver. Here, we first propose a second-order accurate, grid-converging interface curvature estimation, and then adapt it to a fast pressure-correction method (FastP*) \cite{Dodd_JCP_2014} that benefits from an efficient, FFT-based, direct solver. The only additional requirement from \cite{Dodd_JCP_2014} is that the computational domain is periodic in at least two directions. 
\Ge{To efficiently solve for the pressure, we further combine the GFM with a fast pressure-correction method (FastP*) \citep{Dodd_JCP_2014}. Such a combination enables a direct solve of the pressure Poisson equation using the Gauss elimination in the Fourier space; it is the most efficient when the computational domain is periodic, but it also applies to a range of homogeneous Dirichlet/Neumann boundary conditions via fast sine/cosine transforms \citep{Schumann_JCP_1988}, see \eg a recent open-source distribution \citep{Pedro_CaNS}. Using a second-order accurate, grid-converging interface curvature estimation, we will show that the coupled ICLS/NS solver can handle large density/viscosity contrasts and converges between first and second order in both space and time.}

Finally, a unique challenge to the simulation of colloidal droplets is the modeling of near-field interactions. It is known that two or more colloids can interact via dispersion, surface, depletion, and hydrodynamic forces \citep{Mewis_colloidal}. Apart from the hydrodynamic forces which is determined directly from the NS, and the dispersion forces which arise from quantum mechanical effects, the depletion and surface forces must be modelled. These forces can be either attraction or repulsion and are typically calculated from the gradient of a potential.
\Ge{Based on colloidal theory, we propose a novel hydrodynamic model for the depletion force in the framework of the ICLS/NS solver. Our method relies on two extensions: \textit{i)} extending the single level set (SLS) function to multiple level set (MLS) functions; and \textit{ii)} extending the GFM for computation of the gradient of depletion potential. 
MLS has the benefits that each droplet within a colloidal cluster can be treated individually, is allowed to interact with the other droplets, and is guarded from its own mass loss. MLS also prevents numerical coalescence of droplets when they get too close. The computational complexity, proportional to the number of MLS functions ($l$) and the number of cells in each dimension ($N$), is higher than SLS. However, we note that many techniques exist to reduce the CPU cost and/or memory consumption if $lN^d$ ($d=$ 2 or 3) is large. For detailed implementations of such optimized algorithms we refer to \cite{Peng_JCP_1999,Nielsen_JSC_2006,Brun_JCP_2012}. In the present paper, we will demonstrate the self-assembly of colloidal droplets using one droplet per MLS function.}
%Hence, MLS is needed to determine the interaction forces. Combining with GFM, we propose a novel method to compute the near field interactions in our NS solver. The GFM makes the interaction force sharp and the MLS makes it possible for two droplets to be closer than one grid cell without automatic merging.

@@

\noindent where ${\bm u}={\bm u}({\bm x},t)$ is the velocity field, $p=p({\bm x},t)$ is the pressure field, and $\bm{g}$ is a unit vector aligned with gravity or buoyancy. $\rho_i$ and $\mu_i$ are the density and dynamic viscosity ratios of fluid $i$ ($i=1$ or $2$) and the reference fluid. These properties are \Ge{constant in each phase and} subject to a jump across the interface, which we denote as $[\rho]_\Gamma=\rho_2-\rho_1$ for density and $[\mu]_\Gamma=\mu_2-\mu_1$ for viscosity. For viscous flows, the velocity and its tangential derivatives are continuous on the interface \citep{Liu_JCP_1994}. However, the pressure is discontinuous due to the surface tension and the viscosity jump, \ie
\begin{equation}
    [p]_\Gamma = \frac{1}{We} \kappa + \frac{2}{Re}[\mu]_\Gamma {\bm n}^T \cdot \nabla {\bm u} \cdot {\bm n},
  \label{pressure jump}
\end{equation}
\noindent where $\kappa$ is the interface curvature, and ${\bm n}$ is the normal to the interface.  
If the surface tension coefficient, $\tilde{\sigma}$, varies on the interface the tangential stress is also discontinuous. In this paper, we assume constant and uniform $\tilde{\sigma}$. In Eqs.\ \eqref{NS} and \eqref{pressure jump}, Re, We, and Fr are, respectively, the Reynolds, Weber, and Froude numbers, defined as
\begin{equation}
  \begin{aligned}
    Re = \frac{\tilde{\rho_1} \tilde{U} \tilde{L}}{\tilde{\mu_1}},\quad \quad We = \frac{\tilde{\rho_1} \tilde{U}^2 \tilde{L}}{\tilde{\sigma}},\quad \quad Fr=\frac{\tilde{U}^2}{\tilde{g}\tilde{L}},      
  \label{non-di}    
  \end{aligned}
\end{equation}
\noindent where $\tilde{U}$, $\tilde{L}$, $\tilde{\rho_1}$, $\tilde{\mu_1}$, and $\tilde{g}$ denote the reference dimensional velocity, length, density, dynamic viscosity, and gravitational acceleration. Note that $\rho_1=1$ and $\mu_1=1$ (i.e.\ we define fluid 1 as the reference fluid).

@@

The motion of a fluid interface is governed by the following PDE
\begin{equation}
  \frac{\partial \phi}{\partial t} + {\bm u} \cdot \nabla \phi = 0,
  \label{ls adv}
\end{equation}
where ${\bm u}$ is the flow velocity field. Despite of its simple form, obtaining an accurate and robust solution to Eq.\ \eqref{ls adv} is challenging. For two-fluid problems, state-of-the-art level set transport schemes include the high-order upstream-central (HOUC) scheme \citep{Nourgaliev_JCP_2007}, the weighted essentially non-oscillatory (WENO) scheme \citep{Liu_JCP_1994}, \Ge{the semi-Lagrangian scheme \citep{Strain_JCP_1999}}, or the semi-jet scheme \citep{Velmurugana_AX_2016}. Quantitative comparisons of these schemes in various test cases can be found in \cite{Nourgaliev_JCP_2007, Velmurugana_AX_2016}. We note that the choice of the scheme is case-dependent, \ie depending on the smoothness of the overall level set field or the stiffness of Eq.\ \eqref{ls adv}. For flows involving moderate deformations, HOUC is usually sufficient and most efficient. For more complex flows, WENO or semi-Lagragian/jet schemes combined with grid refinement might be pursed. In the present study, we use either HOUC5 or WENO5 (5 denotes fifth-order accuracy) to evaluate $\nabla \phi$.

%In general, a nonlinear hyperbolic system can be solved with finite difference methods, including total-variation-diminishing (TVD), total-variation-bounded (TVB), essentially non-oscillatory (ENO) \cite{Harten_JCP_1987}, and weighted essentially non-oscillatory (WENO) \cite{Liu_JCP_1994} schemes. These methods have been developed to obtain stable and, in the case of ENO or WENO, high-order-accuracy solutions at the appearance of strong discontinuities, see \eg the text of Lax \cite{Lax_1970} and LeVeque \cite{LeVeque_hyperbolic}, or the lecture notes in high-order methods for computational physics edited by Barth and Deconinck \cite{Barth_notes_computational}. Specifically, 
\sloppy
For the temporal discretization of Eq.\ \eqref{ls adv}, we use a three-stage total-variation-diminishing (TVD) third-order Runge-Kutta scheme \citep{Shu_JCP_1988}. Denoting $f(\phi)=-{\bm u} \cdot \nabla \phi$, it updates $\phi$ from time level $n$ to $n+1$ in three sub-steps
\begin{equation}
  \begin{cases}
    & \phi^1 = \phi^n + \Delta t \cdot f(\phi^n)  \\
    & \phi^2 = \frac{3}{4} \phi^n + \frac{1}{4} \phi^1 + \frac{1}{4} \Delta t \cdot f(\phi^1) \\
    & \phi^{n+1} = \frac{1}{3} \phi^n + \frac{2}{3} \phi^2 + \frac{2}{3} \Delta t \cdot f(\phi^2). \\
  \end{cases}
  \label{SSP-RK3}
\end{equation}
%where $f(\phi)=-{\bm u} \cdot \nabla \phi$. %On a standard staggered grid where scalars are defined at cell centers and vectors are defined at cell faces, $f(\phi)$ is computed at cell centers by using central averaging for ${\bm u}$ and a finite difference method for $\nabla \phi$. For the spatial derivatives $\nabla \phi$, instead of using the abovementioned ENO or WENO schemes, we note that the smoothness of $\phi$ and the linearity of its advection Eq.\ \eqref{ls adv} allows the use of simpler and more efficient upwinding schemes, such as the high order upstream central (HOUC) discretizations. Detailed descriptions of HOUC and its comparisons with WENO in the level set framework for interface tracking can be found in \cite{Nourgaliev_JCP_2007, Desjardins_JCP_2008}. Based on these reports and our tests, we use the HOUC5 to evaluate $\nabla \phi$. As a final note, although HOUC5 is fifth-order accurate, the overall accuracy of $\phi$ is second-order due to central averaging of the velocity field at cell centers.

\Ge{Finally, we note that Eq.\ \eqref{ls adv} does not need to be solved in the entire computational domain, as only the near-zero values are used to identify the interface and compute its curvature. This motivated the so-called narrow band approach \citep{Adalsteinsson_JCP_1995, Peng_JCP_1999}, which localizes the level set to the interface using index arrays. Combined with optimal data structures \citep{Nielsen_JSC_2006,Brun_JCP_2012}, fast computation and low memory footprint may be achieved at the same time. In our implementation, we store all the level set values while only update those in a narrow band, \ie solving $\phi_t+c(\phi){\bm u}\cdot \nabla \phi=0$ with the cut-off function given as}
\begin{equation}
  c(\phi) =
  \begin{cases}
     1 & \textrm{if} \quad  |\phi| < \gamma \\
     0 & \textrm{otherwise}, \\
  \end{cases}
  \label{NB cut-off}
\end{equation}
\Ge{where $\gamma= 6\Delta x$ as additional distance information is required to model droplet interactions (Sec.\ \ref{sec: idrop}). This is equivalent to \cite{Peng_JCP_1999} with a simplified $c(\phi)$.}

@@

%Curvature computation is crucial to interfacial flows in the presence of surface tension \citep{Herrmann_JCP_2008, Desjardins_JCP_2008}, and even more so in our case, when we apply curvature-dependent interface corrections. Inaccurate curvature can result in unphysical spurious currents, as will be shown in Sec.\ \ref{sec: spurious}. 
From Eq.\ \eqref{curv}, the curvature $\kappa$ can be evaluated as
